---
title: "Using Webber"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Webber}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This package is a utility belt for working with Western blot images in R. It's primarily focused on making annotation easier. 


```{r setup}
library(webber)
```

# Getting set up with webber

You need to introduce yourself to webber so that you can more easily pull files from Sharepoint. Fortunately, that's rather simple: just run `wb_setup()`. 
It'll tell you to paste a few lines into your .Rprofile (which it will handily open up for you), and you'll need to add your folder name (which should just be `lastname-firstname`). After you restart R, you should be ready to go (provided you've [introduced yourself to Sharepoint](https://kai.quarto.pub/bok/analysis_setup.html#getting-r-to-talk-to-sharepoint))

# Looking through files

Most of the time I don't really know the exact path of the file I'm looking for. webber makes this easy with `wb_list`:

```{r eval=FALSE}
wb_list("/") |> head()
```

```{r echo=FALSE}
webber:::wb_list_head_example
```

Notice how I didn't have to specify my name - that's because of the introduction that we did earlier. If I wanted to root around in someone else's folder, I could do this:

```{r eval=FALSE}
wb_list("/", user = "arbuiso-alyssa")
```

```{r echo=FALSE}
webber:::wb_list_other_user
```

If you want to drill deeper into a folder, you can do this:

```{r eval=FALSE}
wb_list("/2022-04-20_bupa-dr")
```

```{r echo=FALSE}
webber:::wb_list_drill_down
```

# Getting

When you've found your file or folder of interest, you download it with `wb_get`. I'm going to download a single file, but you can do this with whole folders:

```{r eval = FALSE}
file <- wb_get(
  path = "2022-04-20_bupa-dr/pakt-s473-actin.tif",
  dest = tempfile(),
  overwrite = TRUE
)
```

# Editing

With our file in hand, we can now edit it. For this, we call upon the delightful `magick` R package, which uses `imagemagick` under the hood.

```{r eval=FALSE}
library(magick)
image <- image_read(file)
image
```

```{r echo=FALSE}
library(magick)
image <- image_read("https://kai.rbind.io/wb.tif")
image <- image |> image_convert("png")
image
```

The first part - the hardest part - is cropping it down to size. 

`imagemagick` (henceforth `magick`) specifies that the TOP LEFT corner is (0, 0). So if I do this:

```{r}
image_crop(image, "100x300")
```

I get the upper left hand portion.

If I wanted to offset where the area was (I still want it to be 100x300, say, but I want it closer to the bottom) I can specify an offset:

```{r}
image_crop(image, "100x300+0+100")
```

And if I want it closer to the middle:

```{r}
image_crop(image, "100x300+100+0")
```

So how do you make sure you crop the right portion? Unfortunately I don't have a perfect answer for you. You can do trial and error, or you can bring it into a photo editor and measure the dimensions and coordinates of your crop there. The things we do for reproducibility.

```{r}
cropped <- image_crop(image, "370x100+90+200")
cropped
```

Now it just so happens that this dose response is backward - higher concentrations on the left, lower on the right. I prefer it the other way.

```{r}
flopped <- image_flop(cropped)
flopped
```

Great - we're ready to annotate!

# Annotating

Now, back to webber.

To annotate blot lanes with webber, you need to construct a `tibble` with one row per lane, and one column per line of annotation.

```{r}
library(tibble)
# Why a tibble and not a regular data.frame?
# tibbles preserve spaces in their column names, which makes them display nicer.
annot <- 
  tibble(
    "Cell line" = "UC6",
    "Buparlisib (nM)" = c("DMSO", "1", "10", "100", "1000", "10000")
  )
annot
```

Then supply the `tibble` to `wb_annot_lanes`:

```{r}
wb_annot_lanes(flopped, annot, n_lanes = 6, text_size = 4)
```

